---
title: "Ploty"
---

```{r setup, message=FALSE}
library(tidyverse)
library(viridis)
library(plotly)
library(p8105.datasets)
data(ny_noaa)
```

```{r}
nynoaa <- 
  ny_noaa %>% 
  janitor::clean_names() %>%
  separate(date, into = c("Year", "Month", "Day"), sep = "-") %>% 
  janitor::clean_names() 

```
The dataset has has `r nrow(ny_noaa)` rows and `r ncol(ny_noaa)` columns. The dataset contains `r colnames(ny_noaa)` variables.


###ploty 1
```{r}
ny_df_1 =
  nynoaa %>% 
  group_by(year,id) %>% 
  mutate(tmax = as.numeric(tmax)) %>% 
  mutate(tmin = as.numeric(tmin)) %>% 
  na.omit() %>% 
  summarise(mean_temp = mean(tmax/10)) %>% 
  ungroup %>% 
  ggplot(aes(x= year, y = mean_temp, fill = year))+
  geom_boxplot()+
  theme(legend.position = "bottom")+
  ggtitle("The temperature change in every year")

ggplotly(ny_df_1)


```

For plot1, I calculated the mean of maximum temperature, because I hope to compare whether the temperature is increasing from 1981 to 2010. From this plot, these years have similar maximum temperature, except in 1991, this year had higher temperature than other years.


###ploty 2
```{r}
ny_df_2 =
  nynoaa %>% 
  group_by(month,id) %>% 
  mutate(tmax = as.numeric(tmax)) %>% 
  mutate(tmin = as.numeric(tmin)) %>% 
  na.omit() %>% 
  summarise(mean_temp = mean(tmax/10)) %>% 
  ungroup %>% 
  ggplot(aes(x=month, y=mean_temp, color=month))+
  geom_point(alpha = 0.5)+
  theme(legend.position = "bottom")+
  ggtitle("The Temparature Change During a Year")
  
ggplotly(ny_df_2)

```
The second plot, I choose use scatterplot to explore the changing of temperature during a year. In this plot, we can observe it had highest temperature in July, because it is in summer. The lowerest temperature is in Januarary. This plot could explore the trend of temperature clearly. 


###plot 3
```{r}
ny_df_3 <-nynoaa %>% 
  group_by(year, month) %>% 
  na.omit(tmax) %>% 
  na.omit(tmin) %>% 
  mutate(tmax_2 = as.numeric(tmax, na.rm = TRUE)) %>% 
  mutate(tmin_2 = as.numeric(tmin, na.rm = TRUE)) %>%
  ungroup %>% 
  ggplot(aes(tmin_2,tmax_2))+
  geom_hex(bins = 15)+
  theme(legend.position = "bottom")+
  ggtitle("the maximum temperature VS the minimum temperature")

ggplotly(ny_df_3)
```
The third plot, I hope to explore the what is the most counts value for maximum temperature and minimum temperature. This plot has shown the light blue is the most value of temperature and the drak blue is the least value of temperature. When the tmax is about 250 and tmin is about 200, it had the most counts. 